Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-19 manuscript.tex
Condition for division should be >=
Included the pre-reserved DOIs
Say that D=0 means no divisions
Removed  hyperref because it was causing problems

\pdfoutput=1
\documentclass[paper,twocolumn,twoside]{geophysics}
%\documentclass[manuscript]{geophysics}
%\documentclass[manuscript,endfloat]{geophysics}
%\documentclass[twocolumn]{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

@@

\hypersetup{
    colorlinks=true,
    citecolor=blue,
    linkcolor=blue,
    urlcolor=blue,
    pdfauthor={Uieda et al.},
    pdftitle={Tesseroids: forward modeling gravitational fields in spherical
              coordinates}
}
\title{
    Tesseroids: forward modeling gravitational fields in spherical coordinates
}
\author{
    Leonardo Uieda\footnotemark[1]\footnotemark[2],
    Val\'eria C. F. Barbosa\footnotemark[2],
    and
    Carla Braitenberg\footnotemark[3]
}

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in version 1.2 of the open-source package \emph{Tesseroids}.
It is freely available online\footnote{
\url{http://tesseroids.leouieda.com}}\footnote{
\url{}\todo[inline]{Zenodo DOI}}
under the BSD 3-clause open-source license.
An archived version of the source code
is also available as part of this article.

@@

\begin{equation}
    \frac{d}{L_i} > D,
    \label{eq:condition}
\end{equation}

@@

The IPython notebooks
and the data generated for the error analysis,
as well as instructions for installing the software
and running the programs,
are also included in
the source code archive that accompanies this article.
Alternatively,
all accompanying material is available
in online repositories\footnote{
\url{https://github.com/pinga-lab/paper-tesseroids}}\footnote{
\url{}\todo[inline]{Replace with the Zenodo/figshare DOI for the repository.}}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/distance-size-curves}
    \caption{
        The maximum difference between the computed tesseroid and shell effects
        as a function of the distance-size ratio $D$
        for (a) the gravitational potential, (b) $g_z$, and (c) $g_{zz}$.
        The difference is given as a percentage of the shell effect.
        Curves correspond to the different tesseroid models and computation
        grids shown in Table~\ref{tbl:experiment}.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
    }
    \label{fig:dist-size-curves}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/gzz-with-height}
    \caption{
        Difference between the computed $g_{zz}$ for the spherical shell and
        the tesseroid model at different heights. Curves show the maximum
        difference as a percentage of the shell value.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
    }
    \label{fig:gzz-with-height}
\end{figure}

>>>>

\pdfoutput=1
\documentclass[paper,twocolumn,twoside]{geophysics}
%\documentclass[manuscript]{geophysics}
%\documentclass[manuscript,endfloat]{geophysics}
%\documentclass[twocolumn]{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

@@

\title{
    Tesseroids: forward modeling gravitational fields in spherical coordinates
}
\author{
    Leonardo Uieda\footnotemark[1]\footnotemark[2],
    Val\'eria C. F. Barbosa\footnotemark[2],
    and
    Carla Braitenberg\footnotemark[3]
}

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in version 1.2 of the open-source package \emph{Tesseroids}.
It is freely available online\footnote{
http://tesseroids.leouieda.com}\footnote{
http://dx.doi.org/10.5281/zenodo.16033}
under the BSD 3-clause open-source license.
An archived version of the source code
is also available as part of this article.

@@

\begin{equation}
    \frac{d}{L_i} \geq D,
    \label{eq:condition}
\end{equation}

@@

The IPython notebooks
and the data generated for the error analysis,
as well as instructions for installing the software
and running the programs,
are also included in
the source code archive that accompanies this article.
Alternatively,
all accompanying material is available
in online repositories\footnote{
https://github.com/pinga-lab/paper-tesseroids}\footnote{
http://dx.doi.org/10.5281/zenodo.16032}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/distance-size-curves}
    \caption{
        The maximum difference between the computed tesseroid and shell effects
        as a function of the distance-size ratio $D$
        for (a) the gravitational potential, (b) $g_z$, and (c) $g_{zz}$.
        The difference is given as a percentage of the shell effect.
        Curves correspond to the different tesseroid models and computation
        grids shown in Table~\ref{tbl:experiment}.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:dist-size-curves}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/gzz-with-height}
    \caption{
        Difference between the computed $g_{zz}$ for the spherical shell and
        the tesseroid model at different heights. Curves show the maximum
        difference as a percentage of the shell value.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:gzz-with-height}
\end{figure}
